Insertion Sort Analysis in Java

### 2015-02-04 Programming Project A/Insertion Sort Analysis in Java.tex
finished experimental analysis section

The expected growth of insertion sort as the number of elements (n) grows large can be represented as $ \theta(n^2) $ where $ \theta() $ represents the asymptotically tightly bound running time. At $n_0$ the algorithm took 0.0003 milliseconds to complete. At $n_1$ the algorithm also took 0.0003 milliseconds to complete. For both these values of $n$, the algorithm runs at a constant time because no for-loops are executed. As $n$ grows larger the time to complete the experimental data correlates quite accurately with the expected growth. For $n_{1*10^6} $ the data matches up perfectly. This is to be expected however, because as n grows larger the constants and lower orders of the actual running time of the insertion sort start to effect the the running time less and less because the highest order of $n^2$ is so large. 
%% END EXPERIMENTAL ANALYSIS

>>>>

The expected growth of insertion sort as the number of elements (n) grows large can be represented as $ \theta(n^2) $ where $ \theta() $ represents the asymptotically tightly bound running time. At $n_0$ the algorithm took 0.0003 milliseconds to complete. At $n_1$ the algorithm also took 0.0003 milliseconds to complete. For both these values of $n$, the algorithm runs at a constant time because no for-loops are executed. As $n$ grows larger the time to complete the experimental data correlates quite accurately with the expected growth. For $n_{1*10^6} $ the data matches up perfectly. This is to be expected however, because as n grows larger the constants and lower orders of the actual running time of the insertion sort start to effect the the running time less and less because the highest order of $n^2$ is so large. It is expected for lower values of n to not correlate well with $ \theta(n^2) $ because the system running the algorithm may be executing superfolous commands such as checking for system. For the data graphed above (see Fig. 1) this was in fact the case. To aid this issue, averages of 10 trails were taken and used in Figure 1.
%% END EXPERIMENTAL ANALYSIS
